\section{Validation rules}

To validate the internal consistency of the model we list $20$ rules that we have successfully tested.
On the one hand these rules are balance sheet accounting identities, and on the other they are 
conservation rules for material quantities and monetary values. Having thus validated the model
we are confident that the EURACE model is stock-flow consistent, and can form a solid basis for further extensions in the future.

\subsubsection*{Balance sheet identities}

\subsubsection*{RULE 1}
Firm balance sheet: assets and liabilities.

\bigskip
\url{firm_payment_account + firm_total_value_local_inventory + firm_total_value_capital_stock = firm_total_debt + firm_equity}

\subsubsection*{RULE 2}
IGFirm balance sheet: assets and liabilities, all net profits are paid in dividends.

\bigskip
\url{igfirm_net_profit = igfirm_dividend_per_share*igfirm_shares_outstanding}

\subsubsection*{RULE 3}
Bank balance sheet: assets and liabilities.

\bigskip
\url{bank_cash + bank_credit = bank_equity + bank_ecb_debt + bank_deposits}

\subsubsection*{RULE 4}
Government total debt is the value of its outstanding bonds.

\bigskip
\url{gov_total_debt = gov_value_bonds*govt_outstanding_bonds}

\subsubsection*{RULE 5}
ECB: The issued fiat money to government(s) equals the total value of bond holdings of the ECB.

\bigskip
\url{ecb_bond_holdings_value + ecb_cash = ecb_fiat_money_govs + ecb_fiat_money_banks}

\subsubsection*{Aggregates across sectors}

\subsubsection*{RULE 6}
Payment accounts: aggregate bank deposits equals the sum of payment accounts in agent memory.

\bigskip
\url{bank_deposits = firm_payment_account + igfirm_payment_account + hh_payment_account}

\subsubsection*{RULE 7}
Credit money: aggregate Bank credit outstand equals total loans to firms.

\bigskip
\url{bank_credit = firms_total_loans}

\subsubsection*{RULE 8}
Definition of GDP.

\bigskip
\url{eurostat_monthly_gdp = eurostat_monthly_investment_value + household_expenditure + govt_monthly_cons_expenditure}

\subsubsection*{RULE 9}
Total number of shares outstanding equals the total number of shares in household portfolios.

\bigskip
\url{household_assets = firm_current_shares_outstanding + igfirm_shares_outstanding + bank_current_shares_outstanding + govt_outstanding_bonds}

\subsubsection*{RULE 10}
Debt installment payments by firms to banks and received by banks are equal.
\url{firm_debt_installments = bank_loan_installments}

\subsubsection*{RULE 11}
Interest payments by firms to banks and received by banks are equal.

\bigskip
\url{firm_interest_payments_to_banks = bank_interest_payments_from_firms}

\subsubsection*{RULE 12}
Taxes paid and received are equal.

\bigskip
\url{govt_monthly_tax_revenues = firm_tax_payment + igfirm_tax_payment + household_tax_payment + bank_tax_payment}

\subsubsection*{RULE 13}
Deposits at ECB.

\bigskip
\url{ecb_deposits = bank_payment_account + gov_payment_account}

\subsubsection*{RULE 14}
Check the number of active firms.

\bigskip
\url{eurostat_no_firms = firm_active + eurostat_no_firm_bankruptcies}

\subsubsection*{RULE 15}
Daily dividend payments send and received are equal.

\bigskip
\url{firm_total_dividends + igfirm_total_dividends + bank_total_dividends = household_dividend_daily}

\subsubsection*{RULE 16}
Material quantity conservation rule: Eurostat total sold quantity compared with firm data on number of goods sold (in volume).

\bigskip
\url{eurostat_monthly_sold_quantity = firm_total_sold_quantity_volume}

\subsubsection*{RULE 17}
Investments in monetary value: Eurostat data (aggregated across the firms' investment costs) equals the IGFirm revenues.

\bigskip
\url{eurostat_monthly_investment_value = igfirm_revenues}

\subsubsection*{RULE 18}
The Banks' aggregate ECB debt is found on the ECB balance sheet (\url{fiat_money_banks}, LHS), and on the banks' balance sheet (\url{bank_ecb_debt}, RHS). Similarly, the governments' debts are on the ECB balance sheet (\url{fiat_money_govs}, LHS), and equals the value of the ECB bond holdings (\url{bond_holdings_value}, RHS).

\bigskip
\url{ecb_fiat_money_banks + ecb_fiat_money_govs = ecb_bond_holdings_value + bank_ecb_debt}

\subsubsection*{RULE 19}
ECB fiat money is by definition the sum of the fiat money created for governments and for banks.

\bigskip
\url{ecb_fiat_money = ecb_fiat_money_govs + ecb_fiat_money_banks}

\subsubsection*{RULE 20}
Monetary conservation rule
All deposits in the banking sector plus bank equity, plus the money in the public sector (government payment account), 
should equal the credit money created by the banks plus the fiat money created by the central bank.

\bigskip
\url{bank_deposits + bank_equity + gov_payment_account + ecb_cash == bank_credit + ecb_fiat_money}
